### 2013-09-20 inst/doc/manuscript.Rmd
writing

@@

Writing in authorship/publication information, copyright.
Writing in methodological information

>>>>

One of the most powerful features of the NeXML format is the ability add arbitrary metadata information using the RDFa annotation standard [cite W3C]().

Metadata from treebase NeXML
- article citation information
- Summary data: taxa, number of taxa, number of trees, number of tips.  
- Metadata of nodes, complete RDF extraction

@@

`RNeXML` also helps users add richer metadata when producing NeXML files. This occurs on several levels:

- Automatic annotation.  `RNeXML` automatically adds basic metadata by default such as a timestamp of when the tree was produced and an open data license (CC0, compatible with deposition on Dryad data repository), which can be configured as needed.

- Utilities to add common metadata

  - Add a citation to any papers associated with the phylogeny data.  
  - Writing in methodological information on how tree has been generated or analyzed (including R code)
  - Add annotations to any taxon.
